%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Thales}{May 2022 -- Present}
    {Cloud Architect}{Vélizy-Villacoublay}
    \resumeItemListStart
        \resumeItem{Built Kubernetes/RKE2/Rancher clusters on OpenStack tenants to migrate old client' apps hosted on VMs. Improved response times to up to 50\% faster. Met scaling, and disaster recovery requirements.}
        \resumeItem{Managed production environments with 5 large Debian Hypervisors (256GB RAM, Terabytes of disk..) using Dell IDRACs and PXE.}
        \resumeItem{Designed development environments to meet the production architecture (ISO-prod dev environments). Used Terraform and Ansible to reduce the deployment time to an avg of 7min (vs avg 15min using the old method).}
    \resumeItemListEnd
    
    \resumeSubheading
    {kShuttle}{Oct 2019 -- Apr 2O22}
    {DevOps Engineer}{Levallois-Perret}
    \resumeItemListStart
        \resumeItem{Automated 113 non-regression test scenarios using Jenkins, Cypress/Node, Java, and Selenium.}
        \resumeItem{Designed and built CI/CD pipelines for Lease management projects for more than 70 clients using Jenkins, Docker, Kubernetes, and Rancher.}
        \resumeItem{Built performance tests pipeline using Jenkins and Elastic Stack.}
    \resumeItemListEnd

    \resumeSubheading
    {Konvergence B\&T}{Feb 2019 -- Sep 2019}
    {DevOps Engineer -- Intern}{Levallois-Perret}
    \resumeItemListStart
        \resumeItem{Containerized 7 client apps. Setup a private registry and managed client deployments using Rancher. }
        \resumeItem{Designed and built Security test pipelines for 2 apps using Jenkins, OWASP ModSecurity, and Elastic Stack.}
        \resumeItem{Implemented CI/CD pipelines for company Core project.}
    \resumeItemListEnd

\resumeSubHeadingListEnd